%-------------------------
% Resume in Latex
% Author : Pramodh Ugargol
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Pramodh Ugargol} \\ \vspace{1pt}
    \small 9108260219 $|$ \href{mailto:pramram.18@gmail.com}{\underline{pramram.18@gmail.com}} $|$ 
    \href{https://linkedin.com/in/pramodhugargol18}{\underline{linkedin.com}} $|$
    \href{https://github.com/PRAMOMDHUGARGOL/}{\underline{github.com}} $|$ \href{https://portfolio-pramodh-ugargol.vercel.app/}{\underline{Portfolio}}
\end{center}

%-----------PROFILE SUMMARY-----------
\section{Profile Summary}
As a creative technologist and dedicated developer, I bring three years of experience in crafting comprehensive web applications from start to finish. I'm enthusiastic about collaborating with diverse and dynamic teams to apply my skills and broaden my knowledge.



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, HTML, CSS, Python, C, C++ } \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Express.js, Flask, MaterialUI, Bootstrap, TailwindCSS} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, VS Code, Chrome DevTools, Eclipse, MATLAB} \\
    \textbf{Libraries}{: Redux, Stripe.js, OpenCV, pandas, NumPy, Matplotlib}\\
    \textbf{Databases}{: Firebase, Google Sheets} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Software Engineer}{Aug 2021 -- Present}
{Alltramatic}{New York, USA (Remote)}
\resumeItemListStart
\resumeItem{Engineered reusable \textbf{React} higher-order components \textbf{(HOCs)} enhancing code maintainability and consistency. 
}
\resumeItem{Managed components with robust state management, leveraging \textbf{Redux} and \textbf{React Hooks}.}
\resumeItem{Led the strategic migration of the entire codebase from React to \textbf{Next.js}, enhancing \textbf{SEO} coverage.}
\resumeItem{Maintained code stability across applications through rigorous testing and debugging using diverse \textbf{TDD} practices}
\resumeItem{Created scalable and efficient server-side applications using \textbf{Express.js} and \textbf{Node.js}.}
\resumeItem{Improved performance through cost-efficient \textbf{Firebase} NoSQL structure, minimizing reads for enhanced efficiency.}
\resumeItem{Played a pivotal role in exponential business expansion, attracting and retaining over \textbf{100+} customers.}
\resumeItemListEnd
\vspace{5pt} % Adjust the space measurement as needed

\resumeSubheading
{Software Engineer Intern}{Mar 2021 -- Aug 2021}
{Alltramatic}{New York, USA (Remote)}
\resumeItemListStart
\resumeItem{Implemented a shortest path traversal feature for autonomous vehicle navigation between two designated points.}
\resumeItem{Developed \textbf{Tkinter}-based simulations to showcase performance enhancements in shortest path traversal.}
\resumeItem{Contributed to \textbf{documentation} and knowledge-sharing sessions within the team.}
\resumeItemListEnd
\resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
   
      \resumeProjectHeading
        {\textbf{Lawnber} $|$ \emph{React, Node.js, Firebase, Express.js, Stripe.js, MaterialUI} $|$ \hfill \href{https://lawnber.com}{\underline{Link}}}


          \resumeItemListStart
           \resumeItem{Developed a seamless sign up process featuring \textbf{responsive} subscription plans and Credit Card component. }
           \resumeItem{Implemented user impersonation feature using Firebase authentication and tokens, enhancing admin capabilities.}
            \resumeItem{Created a component to manage credit card functionality, including addition, deletion and prioritization.}
          \resumeItemListEnd
          
      \resumeProjectHeading
         {\textbf{NYU Student Rental} $|$ \emph{Next.js, Node.js, Firebase, Express.js, TailwindCSS} $|$ \hfill \href{https://nyustudentrent.com}{\underline{Link}}}

          \resumeItemListStart
            \resumeItem{Designed and implemented a fully responsive website from scratch, ensuring compatibility across all devices.}
            \resumeItem{Developed a listings page showcasing available rentals and a submission page for student inquiries.}
             \resumeItem{Developed a blog creation page within the admin site to add and display blogs retrieved from a Firebase database.}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Custom Video Player} $|$ \emph{Next.js, TailwindCSS}$|$ \hfill \href{https://vid-player-wheat.vercel.app/}{\underline{Link}}}\
          \resumeItemListStart
            \resumeItem{Enhanced user experience with intuitive features like playlist navigation and search, improving engagement}
            \resumeItem{Implemented drag-and-drop for playlist organization, enabling effortless video rearrangement}
            
          
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Certifications}
{\small
\begin{itemize}

    \item \textbf{Introduction to Front-End Development (Meta)} $|$ \href{https://coursera.org/share/d7e6b6db2f29dc5ccd3b8409f28c66a5} {\underline{Certificate}}
    {\hfill March 2024}
    \item \textbf{Programming with JavaScript (Meta)} $|$  \href{https://coursera.org/share/d7e6b6db2f29dc5ccd3b8409f28c66a5} {\underline{Certificate}}
    {\hfill March 2024}
    \item \textbf{Version Control (Meta)} $|$   \href{https://coursera.org/share/d7e6b6db2f29dc5ccd3b8409f28c66a5} {\underline{Certificate}}
    {\hfill March 2024}
\end{itemize}
}

%
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Visvesvaraya Technological University (VTU)}{Belgaum, Karnataka}
{Bachelor of Engineering in Electronics and Communications}{Aug 2017 -- Aug 2021}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
